\documentclass {phresume}
\setprop {name} {Zhixian Huang}
\setprop {email} {hzx1991@gmail.com}
\setprop {phone} {(669)999-0356}

\begin {document}
\begin {section} {Summary}
\desc {Software Engineer in Juniper Networks Inc.}
\desc {Strong experience on Unix/Linux kernel development and Android system bring up.}
\desc {Familiar with Computer Networking, Computer Architecture, Robotics, Systems Security.}
\desc {Language: C/C++, Python, Shell Script.}
\end {section}

\begin {section} {Employment}
\timeline {Software Engineer} {02/2018} {present}
\text {Juniper Networks Inc., Sunnyvale, California}
\desc {Contribute system level features and supports on enterprise networking devices in the platform team.}
\desc {Lead six mini projects across four new products, including SRX-SPC3, SRX-RE3 and ACX7100.}
\desc {Involve in expertise of device firmware, system resiliency and hardware diagnostics.}
\sep

\timeline {Embedded Systems Engineer} {05/2015} {02/2018}
\text {Rufus Labs Inc., Los Angeles, California}
\desc {Brought up a wearable device starting from designing its schematics.}
\desc {Wrote drivers for subsystems including display, power management, sensors, and other peripherals.}
\desc {Ported Android Marshmallow and got it running on the product.}
\desc {Maintained the Android code base and supporting the application team on system related issues.}
\sep

\timeline {Research \& Development Engineer} {10/2013} {06/2014}
\text {Shenzhen MinDe Electronics Technology Ltd., Shenzhen, China}
\desc {Developed applications for barcode scanners based on customer’s request.}
\desc {Integrated on-board database on device.}
\desc {Added Unicode supports for products.}
\end {section}

\begin {section} {Projects}
\text {Single Foot Balance of Humanoid Robot}
\desc {Achieved balancing task on a humanoid robot with 25 Degrees of Freedom.}
\desc {Implemented code of trajectory planning, inverse kinematics, PID controller and Kalman filter.}
\desc {Fine-tuned the robot to step in place continuously and smoothly.}
\sep

\text {Weenix Operating System Kernel Implementation}
\desc {Developed a primitive kernel for a UNIX-like operating system.}
\desc {Wrote major components including process \& thread, virtual file system, and virtual memory.}
\desc {Realized running multiple applications concurrently on this system.}
\end {section}

\begin {section} {Education}
\timeline {M.S. in Electrical Engineering (GPA: 3.60/4.0)} {08/2014} {05/2016}
\text {University of Southern California, Viterbi School of Engineering}
\sep

\timeline {B.E. in Telecommunications Engineering (GPA: 3.67/4.0)} {09/2009} {07/2013}
\text {Shenzhen University, College of Information Engineering}
\end {section}

\end {document}
